### 2019-10-17 tesis_hiram/Chapter2/chapter2.tex
final

%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Second Chapter *********************************
%*******************************************************************************

@@

The LHC is designed to accelerate particles to high energies and generate collisions. There are several
experiments installed along the LHC ring. One of them is ATLAS, located on Point 1 between the two injection lines , which is a general purpose detector. At point 5 is another general purpose detector: the compact muon solenoid  (CMS). A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
\\

Inside the accelerator, two high energy particles beams travel at
close to the speed of light before they collide. 
In order to make them collide, beams travel in opposite directions in separate beam pipes, 
two tubes kept at ultrahigh vacuum. 
By using of superconducting electromagnets that generates a powerful magnetic field , the beams are guided around the accelerator ring. 
The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.For that, it is required to have  magnets to a temperature of  $‑271.3$ C. 
To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}

@@

Protons in the LHC start out as hydrogen atoms stripped of their electrons. The first accelerating stage the protons are subjected to is a linear accelerator, Linac2,
which accelerates them up to 50 MeV . The protons are then sent into the
Proton Synchotron Booster which accelerates them up to 1.4 GeV before sending them to the Proton Synchotron (PS). The protons leave the PS at 25 GeV before entering the Super Proton Synchotron (SPS), which accelerates them to the LHC injection energy of 450 GeV. After this stage, the beam is ready to be injected into
the LHC through one of two injection lines with 6.5 TeV.\cite{cern3}

\begin{table}[!htbp]
\centering
	\caption{Accelerator operation energies\cite{cern3,cern1}}
	\begin{tabular}{|c|c|}
		\hline
		Accelerator & Energy \\
		\hline
		Linac 2 &  50 MeV \\
		\hline
		PS Booster & 1.4 GeV \\
		\hline
		Proton Scyncroton (PS) & 25 GeV\\
		\hline
		SPS &  450 GeV\\
		\hline
		LHC & 6.5 TeV\\
		\hline
	\end{tabular}
\end{table}
\pagebreak
Inside the detectors, collided protons generates an amount of particles such as pion and kaons, which are the most commons, created by the jet particles that were created after the collision. Besides of the particles created by the quarks of the proton , gluons are also radiated and create new particles and photons are radiated too. \\
During the collision time, the main  detectors of LHC capture the energy 
and save the data in supercomputers. Those high end computers starts to measure the signals in order to assign a type of events.
\\

@@

The CMS experiment is composed of several detector layers  that allow identify and save different types of energy signals  and it is saved in a powerful supercomputers that separate and classify the data according to certains variables. The general parts of the CMS are the Silicon Tracker , an Electromagnetic Calorimeter,a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector. \\

@@

The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillanting crystals (emits light when particles interact with the crystal). These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps. The barrel section  of the ECAL covers the range $|\eta| < 1.479$. The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face. The crystal length is 230 mm.The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\

The endcaps cover have the  range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has  identically shaped crystals grouped in
mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$ ,and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/ecal.png}
	\caption{View of the ECAL\cite{cms-manual}}\label{ecal}
\end{figure}
In the barrel, there photo detectors called avalanche photo diodes (APD), made of silicon with a active area of  5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.  At the endcap , the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$) , allowing to operate in the magnetic field. VPT have a size of 25 mm in diameter , glued to the back of each crystal.\\

There is also a preshower detector , which principal function  is to identify neutral pions in the
endcaps within the region 1.653 < |$\eta$| < 2.6. It also helps the identification of electrons
against minimum ionizing particles, and improves the position determination of electrons and photons.
\\

@@

The HB is an assembly of two half barrels, composed of 18 wedges.Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel).Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087. Light of scintillator is collected by a single wave
length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm. 
\\

HE is composed by brass absorber plates ,with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.  HE is sectioned in 5 in $\phi$ to match the barrel wedges.
 . %HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is , the geometry of the barrel muon system. Divided by 5 rings of 2.54 wide, composed of the scintillators on either side of the tail catcher iron of 18cm thick at radial distances of 3850 and 4097 mm respectively. \cite{cms-manual} 
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/hcal.png}
	\caption{View of the CMS HCAL showing the different layers and tower regions. In the endcap, the towers are defined with two longitudinal segments as shown by the colors\cite{cms-manual}}\label{hcal}
\end{figure}
The outer barrel hadron calorimeter (HO) consists of layers of scintillator with  thickness of 10 mm, located outside of the
magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.\\
There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
steel absorbers and embedded radiation hard quartz fibers,which collects 
Cherenkov light\cite{cms-manual}.% that is  when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 
%The length of the fibers are 1.65 m and 1.43 m, which are alterned with a 5 mm of separation. 
\\

@@

The HCAL measures the energy of hadrons,such as the pions and kaons. 
The energy resolution of the HCAL was estimated using a test beam of pions. For 100 GeV pions, the resolution obtained is 12$\%$.
 %By using the info given by the HCAL, it is possible reconstruct the track in order to calculate the momentum of the particles.

\subsection{Muon Detector}
%The muon detector system  %has 3 primary functions: muon
%triggering, identification, and momentum measurement\cite{cms7}. 
%The process utilized in the CMS muon chamber systems is gas ionization. Those gas-ionization particle detectors are arranged in a cylindrical barrel region and planar endcaps, in order to meet the geometry of the solenoid.The barrel detector is built with 4 layers of 250 chambers inside the magnet return yoke.\cite{cms-manual}
The Muon Detector has three main subdetectors: the drift tubes chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
The  DT's, CSC's and RPC's are shown in the figure \ref{dt}.
 \\

@@

The CSC's are located in the endcap regions 0.9 < $|\eta|$ < 2.4. The CSC's are installed on the face of steel disks perpendicular to the beam. 
Each CSC has a trapezoidal shape and consist of 6 gas gaps between 7 metal plates, where each gap contains  copper cathode strips and anode wires running almost perpendicularly to
the strips, with a diameter of 50 $\mu m$ separated by 3.16 mm.  
%CSC is composed of 6 layers that measures the $\mu$ position in the r-$\phi$ coordinate plane. 
The chambers use a gas mixture of 50$\%$ CO$_2$ , 40 $\%$ Ar and 10$\%$ CF$_4$. The muon endcap system comprises 468 CSCs in the 2 endcaps \cite{cms-manual,cms7}.
%Together with DT, cover the $|\eta|< 2.4$. These systems can each identify the collision crossing that generated the muon and trigger on (recolect) the transverse momentum ($p_T$). 
\\

The RPC are located in the barrel and endcap regions that covers the range o $|\eta|<1.6$. The main purpose is to trigger events with muons. 
RPC's are structured with a double gas filled gap and readout strips between the gaps .\\
 The gas mix used in the RPC consist of 95.2$\%$ Freon
($C_2 H_2 F_4$ ), 4.5$\%$ isobutane ($C_4 H_{10}$), and 0.3$\%$ sulphur hexafluoride (SF$_6$ )\cite{cms7}.\\

 %The vertical lines represent the endcap and the horizontal the muon barrel. The orange sections are the DTs , where the 4 DTs are labeled MB,CSC marked in green are labeled ME or muon endcap and RPC are the blue lines that are located in the barrel and the endcap. RPC are labeled RB and RE respectively.

>>>>

%!TEX root =../thesis. Tex
%*******************************************************************************
%****************************** Second Chapter *********************************
%*******************************************************************************

@@

The LHC is designed to accelerate particles to high energies and generate collisions. There are several
experiments installed along the LHC ring. One of them is ATLAS, located on Point 1 between the two injection lines, which is a general purpose detector. At point 5 is another general purpose detector: the compact muon solenoid (CMS). A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
\\

Inside the accelerator, two high energy particles beams travel at
close to the speed of light before they collide. 
In order to make them collide, beams travel in opposite directions in separate beam pipes, 
two tubes kept at ultrahigh vacuum. 
By using of superconducting electromagnets that generates a powerful magnetic field, the beams are guided around the accelerator ring. 
The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy. For that, it is required to have magnets to a temperature of $‑271.3$ C. 
To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}

@@

Protons in the LHC start out as hydrogen atoms stripped of their electrons. The first accelerating stage the protons are subjected to is a linear accelerator, Linac2,
which accelerates them up to 50 MeV. The protons are then sent into the
Proton Synchotron Booster which accelerates them up to 1.4 GeV before sending them to the Proton Synchotron (PS). The protons leave the PS at 25 GeV before entering the Super Proton Synchotron (SPS), which accelerates them to the LHC injection energy of 450 GeV. After this stage, the beam is ready to be injected into
the LHC through one of two injection lines with 6.5 TeV.\cite{cern3}

\begin{table}[!htbp]
\centering
	\caption{Accelerator operation energies\cite{cern3,cern1}}
	\begin{tabular}{|c|c|}
		\hline
		Accelerator & Energy \\
		\hline
		Linac 2 & 50 MeV \\
		\hline
		PS Booster & 1.4 GeV \\
		\hline
		Proton Scyncroton (PS) & 25 GeV\\
		\hline
		SPS & 450 GeV\\
		\hline
		LHC & 6.5 TeV\\
		\hline
	\end{tabular}
\end{table}
\pagebreak
Inside the detectors, collided protons generates an amount of particles such as pion and kaons, which are the most commons, created by the jet particles that were created after the collision. Besides of the particles created by the quarks of the proton, gluons are also radiated and create new particles and photons are radiated too. \\
During the collision time, the main detectors of LHC capture the energy 
and save the data in supercomputers. Those high end computers starts to measure the signals in order to assign a type of events.
\\

@@

The CMS experiment is composed of several detector layers that allow identify and save different types of energy signals and it is saved in a powerful supercomputers that separate and classify the data according to certains variables. The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter, a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector. \\

@@

The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillanting crystals (emits light when particles interact with the crystal). These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps. The barrel section of the ECAL covers the range $|\eta| < 1.479$. The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face. The crystal length is 230 mm. The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\

The endcaps cover have the range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has identically shaped crystals grouped in
mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/ecal.png}
	\caption{View of the ECAL\cite{cms-manual}}\label{ecal}
\end{figure}
In the barrel, there photo detectors called avalanche photo diodes (APD), made of silicon with a active area of 5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal. At the endcap, the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$), allowing to operate in the magnetic field. VPT have a size of 25 mm in diameter, glued to the back of each crystal.\\

There is also a preshower detector, which principal function is to identify neutral pions in the
endcaps within the region 1.653 < |$\eta$| < 2.6. It also helps the identification of electrons
against minimum ionizing particles, and improves the position determination of electrons and photons.
\\

@@

The HB is an assembly of two half barrels, composed of 18 wedges. Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel). Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087. Light of scintillator is collected by a single wave
length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm. 
\\

HE is composed by brass absorber plates, with the thickness of 78 mm, and a total of 19 scintillator layers with a thickness of 3.7 mm. HE is sectioned in 5 in $\phi$ to match the barrel wedges.
. %HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is, the geometry of the barrel muon system. Divided by 5 rings of 2.54 wide, composed of the scintillators on either side of the tail catcher iron of 18cm thick at radial distances of 3850 and 4097 mm respectively. \cite{cms-manual} 
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/hcal.png}
	\caption{View of the CMS HCAL showing the different layers and tower regions. In the endcap, the towers are defined with two longitudinal segments as shown by the colors\cite{cms-manual}}\label{hcal}
\end{figure}
The outer barrel hadron calorimeter (HO) consists of layers of scintillator with thickness of 10 mm, located outside of the
magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.\\
There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
steel absorbers and embedded radiation hard quartz fibers, which collects 
Cherenkov light\cite{cms-manual}.% that is when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 
%The length of the fibers are 1.65 m and 1.43 m, which are alterned with a 5 mm of separation. 
\\

@@

The HCAL measures the energy of hadrons, such as the pions and kaons. 
The energy resolution of the HCAL was estimated using a test beam of pions. For 100 GeV pions, the resolution obtained is 12$\%$.
 %By using the info given by the HCAL, it is possible reconstruct the track in order to calculate the momentum of the particles.

\subsection{Muon Detector}
%The muon detector system %has 3 primary functions: muon
%triggering, identification, and momentum measurement\cite{cms7}. 
%The process utilized in the CMS muon chamber systems is gas ionization. Those gas-ionization particle detectors are arranged in a cylindrical barrel region and planar endcaps, in order to meet the geometry of the solenoid. The barrel detector is built with 4 layers of 250 chambers inside the magnet return yoke.\cite{cms-manual}
The Muon Detector has three main subdetectors: the drift tubes chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
The DT's, CSC's and RPC's are shown in the figure \ref{dt}.
 \\

@@

The CSC's are located in the endcap regions 0.9 < $|\eta|$ < 2.4. The CSC's are installed on the face of steel disks perpendicular to the beam. 
Each CSC has a trapezoidal shape and consist of 6 gas gaps between 7 metal plates, where each gap contains copper cathode strips and anode wires running almost perpendicularly to
the strips, with a diameter of 50 $\mu m$ separated by 3.16 mm. 
%CSC is composed of 6 layers that measures the $\mu$ position in the r-$\phi$ coordinate plane. 
The chambers use a gas mixture of 50$\%$ CO$_2$, 40 $\%$ Ar and 10$\%$ CF$_4$. The muon endcap system comprises 468 CSCs in the 2 endcaps \cite{cms-manual,cms7}.
%Together with DT, cover the $|\eta|< 2.4$. These systems can each identify the collision crossing that generated the muon and trigger on (recolect) the transverse momentum ($p_T$). 
\\

The RPC are located in the barrel and endcap regions that covers the range o $|\eta|<1.6$. The main purpose is to trigger events with muons. 
RPC's are structured with a double gas filled gap and readout strips between the gaps.\\
 The gas mix used in the RPC consist of 95.2$\%$ Freon
($C_2 H_2 F_4$ ), 4.5$\%$ isobutane ($C_4 H_{10}$), and 0.3$\%$ sulphur hexafluoride (SF$_6$ )\cite{cms7}.\\

 %The vertical lines represent the endcap and the horizontal the muon barrel. The orange sections are the DTs, where the 4 DTs are labeled MB,CSC marked in green are labeled ME or muon endcap and RPC are the blue lines that are located in the barrel and the endcap. RPC are labeled RB and RE respectively.

### 2019-10-17 tesis_hiram/Chapter3/chapter3.tex
final

%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Third Chapter **********************************
%*******************************************************************************
\chapter{Event reconstruction and selection}
During the proton collision, many types of processes happen whose information are saved in the CMS data storage system. But the events are only saved if they fulfill certain conditions compatible with the signal. 
For the tH process , the search is based on the presence of  a pair of muons with the same sign. The rest of the processes that also generates a pair of muons with the same sign will be considered backgrounds.  
\section{Signal Event Topology} 
In this search, top quark decays to $Wb$ and from the $W$ boson decays to a muon and a neutrino. The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino. This is the main process that generates events with two same sign muons.The tH process topology is shown in the figure \ref{jet}.\\

@@

  %The W bosons can also decay to quarks that generate jets. 
Due to the small cross section of the $tH$ process, the amount of $tH$ events is low compared to other Higgs production processes. 
Table \ref{tdecay} shows several processes that generate same sign muon events for $t$H. These numbers do not consider the detection efficiency.
  %But also tH process can generate the final states from $\tau$ decays but with a low probability. Some of them have probability near zero , but not impossible . %In graphics, these low probability processes would be very small figures that barely manifest.

@@

\section{Backgrounds}
Several processes contribute to the background in this search:
\begin{itemize}
		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muons comes from a top and the other comes from the vector boson.
			\item $\bm{W^{+}Z}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
		\item $\bm{tZq}$: Processes with single top quarks associated  with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
		\item$\bm{W^{+}W^{-}Z}$, $\bm{ZZZ}$ and $\bm{W^{+}ZZ}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
			\item $\bm{t\bar{t}H}$: This Higgs  production mechanism is considered a background in this analysis. The muons in this cases comes from one top and Higgs decays. 
	\item $\bm{Fakes}$:This background refers to events where two muons come from  $b$ meson decays in jets.
\end{itemize}
Table \ref{back} show the decay chains and production cross section for background. Due to small expected event yields, the processes $W^\pm$ $W^\pm$ ,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$   are grouped as one called Rares in the results below.

@@

\begin{table}[!ht]
	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm , \tau^\pm$.}
	\begin{tabular}{|l|c|c|}
		\hline
		Decay chain & BR & Events\\
		\hline 
		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$  $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} &  1.173  \\
		\hline
		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$  $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$  $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105  \\
		\hline
		\small{$tH \rightarrow W^+ b \tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
		\small{1.681 $\times$10$^{-4}$} & 0.094 \\
		\hline
		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
		\hline
		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q}  b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
		\hline 
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} &  0.008  \\
		\hline
	\end{tabular}
\label{tdecay}
\end{table}

@@

\section{Systematic uncertanties}
\begin{itemize}
\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
\item For the Higgs processes $tH$ and $ttH$ , the uncertainty are due to the theoretical parameters used in that simulation.
\end{itemize}

%control region: event selection with 3 leptons for compare simulation with real data. yield difference  in that region is 50 .is taken  and for wz is 50
%selection that allows to isolate a background  respect to other backgrounds, that background allows to compare with real data

>>>>

%!TEX root =../thesis. Tex
%*******************************************************************************
%****************************** Third Chapter **********************************
%*******************************************************************************
\chapter{Event reconstruction and selection}
During the proton collision, many types of processes happen whose information are saved in the CMS data storage system. But the events are only saved if they fulfill certain conditions compatible with the signal. 
For the tH process, the search is based on the presence of a pair of muons with the same sign. The rest of the processes that also generates a pair of muons with the same sign will be considered backgrounds. 
\section{Signal Event Topology} 
In this search, top quark decays to $Wb$ and from the $W$ boson decays to a muon and a neutrino. The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino. This is the main process that generates events with two same sign muons. The tH process topology is shown in the figure \ref{jet}.\\

@@

 %The W bosons can also decay to quarks that generate jets. 
Due to the small cross section of the $tH$ process, the amount of $tH$ events is low compared to other Higgs production processes. 
Table \ref{tdecay} shows several processes that generate same sign muon events for $t$H. These numbers do not consider the detection efficiency.
 %But also tH process can generate the final states from $\tau$ decays but with a low probability. Some of them have probability near zero, but not impossible. %In graphics, these low probability processes would be very small figures that barely manifest.

@@

\section{Backgrounds}
Several processes contribute to the background in this search:
\begin{itemize}
		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muons comes from a top and the other comes from the vector boson.
			\item $\bm{W^{+}Z}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
		\item $\bm{tZq}$: Processes with single top quarks associated with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
		\item$\bm{W^{+}W^{-}Z}$, $\bm{ZZZ}$ and $\bm{W^{+}ZZ}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
			\item $\bm{t\bar{t}H}$: This Higgs production mechanism is considered a background in this analysis. The muons in this cases comes from one top and Higgs decays. 
	\item $\bm{Fakes}$:This background refers to events where two muons come from $b$ meson decays in jets.
\end{itemize}
Table \ref{back} show the decay chains and production cross section for background. Due to small expected event yields, the processes $W^\pm$ $W^\pm$,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$ are grouped as one called Rares in the results below.

@@

\begin{table}[!ht]
	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
	\begin{tabular}{|l|c|c|}
		\hline
		Decay chain & BR & Events\\
		\hline 
		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$ $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} & 1.173 \\
		\hline
		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$ $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$ $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105 \\
		\hline
		\small{$tH \rightarrow W^+ b \tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$ &
		\small{1.681 $\times$10$^{-4}$} & 0.094 \\
		\hline
		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
		\hline
		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q} b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
		\hline 
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ $\rightarrow$ $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} & 0.008 \\
		\hline
	\end{tabular}
\label{tdecay}
\end{table}

@@

\section{Systematic uncertanties}
\begin{itemize}
\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
\end{itemize}

%control region: event selection with 3 leptons for compare simulation with real data. yield difference in that region is 50. Is taken and for wz is 50
%selection that allows to isolate a background respect to other backgrounds, that background allows to compare with real data
